### 2017-01-05 Plos-one-manuscript/latex/manuscript.tex
editing

Some simple and clever printable parts that have emerged are ones that give a new function to a ubiquitous existing device, such as drill bit attachment designed to hold centrifuge tubes, allowing a dremel to be used as a centrifuge\cite{Garvey2009}.
Although this may make a rather crude centrifuge it may be an adequate solution for a fraction of the cost of a commercial centrifuge.
Other examples of open-design research tools that utilize 3D printed parts include optics equipment\cite{Zhang2013}, microscopes\cite{Baden2014a,Walus2014}, syringe pumps\cite{Wijnen2014}, and reactionware\cite{Symes2012} to name a few.

@@

\section*{Methods}
Our printed pipette is designed to actuate a 1 mL or 3 mL syringe to a user set displacement.
The core of the design is two printed parts, the body and the plunger which are able to be printed on a consumer grade FDM printer (fig.~\ref{fig1}).
A 1 mL or 3 mL syringe twists to lock in the body part and is held into place by the syringe flanges.
The 30-300 $\mu$L configuration uses a 1 mL pipette and the 100-1000 $\mu$L configuration uses a 3 mL pipette.
The plunger part slides freely in the body part and actuates the syringe by pushing the thumb button (fig.~\ref{fig2}). 
The pipette is spring loaded towards a set point which is adjustable by a set-screw.
When the thumb button is pressed the system locks when it reaches the latched position, where it is ready to draw in fluid.
The plunger is held in place with a latching button design which is released with the unlatching button drawing in fluid.
The displacement is equal to the distance between the set position and the latched position.
The pipette can also be pressed past the latched position to `blow-out' the transferred fluid completely from the pipette tip.   
Additional materials required for assembly include two springs, a nut, a bolt and two washers.
Attempts to make a printable luer lock adapter for tips was abandoned as the surface of printed parts is too rough to make an air tight seal with the luer or pipette tip.
Instead, a combination of a barbed luer adapter and elastic tubing is used to attach the pipette tips.
Our printed pipette mimics commercial pipettes design, function, and user operation, making it intuitive to use.

>>>>

Some simple and clever printable parts that have emerged are ones that give a new function to a ubiquitous existing device, such as drill bit attachment designed to hold centrifuge tubes, allowing a dremel to be used as a centrifuge\cite{Garvey2009}.
Although this may make a rather crude centrifuge it may be an adequate solution for a fraction of the cost of a commercial centrifuge.
Other examples of open-design research tools that utilize 3D printed parts include optics equipment\cite{Zhang2013}, microscopes\cite{Baden2014a,Walus2014}, syringe pumps\cite{Wijnen2014}, reactionware\cite{Symes2012} and the list continues to grow.

@@

\section*{Methods}
Our printed pipette is designed to actuate a 1 mL or 3 mL syringe to a user set displacement.
The core of the design is two printed parts, the body and the plunger which are able to be printed on a consumer grade FDM printer (fig.~\ref{fig1}), in this case a Makerbot Replicator.
A 1 mL or 3 mL syringe twists to lock in the body part and is held into place by the syringe flanges.
The 30-300 $\mu$L configuration uses a 1 mL pipette and the 100-1000 $\mu$L configuration uses a 3 mL pipette.
The plunger part slides freely in the body part and actuates the syringe by pushing the thumb button (fig.~\ref{fig2}). 
The pipette is spring loaded towards a set point which is adjustable by a set-screw.
When the thumb button is pressed the system locks when it reaches the latched position, where it is ready to draw in fluid.
The plunger is held in place with a latching button design which is released with the unlatching button drawing in fluid.
The displacement is equal to the distance between the set position and the latched position.
The pipette can also be pressed past the latched position to `blow-out' the transferred fluid completely from the pipette tip.   
Additional materials required for assembly include two springs, a nut, a bolt and two washers.
Attempts to make a printable luer lock adapter for tips was abandoned as the surface of printed parts is too rough to make an air tight seal with the luer or pipette tip.
Instead, a combination of a barbed luer adapter and elastic tubing is used to attach the pipette tips.
Our printed pipette mimics commercial pipettes design, function, and user operation, making it intuitive to use.
